A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-04-03 paper/sections/analysis.tex
Adding analysis and discussion of domains.

\subsection{Research Question 2}

What are the motivations behind RBAC extensions? \\

@@

\subsection{Research Question 3}

Do the extension models have corresponding implementations? \\

@@

\subsection{Research Question 4}

How are extension to RBAC evaluated theoritically and in practice? \\

@@

@@

\subsection{Research Question 5}

What domains have RBAC extensions been created for? \\

Business needs have historically driven RBAC research and development.  The primary mode of evaluation for
model extensions has been the presentation of business scenarios in various domains and how the model
uniquely handles those particular scenarios.  Thus, looking for trends in the domains used in the example
scenarios might serve to illuminate a trend worth further examination into the reason for the explosion of
RBAC extensions.

Upon examination of the primary sources, the most prevalent domains were:

@@

>>>>

RQ2: What are the motivations behind RBAC extensions? \\

@@

RQ3: Do the extension models have corresponding implementations? \\

@@

RQ4: How are extension to RBAC evaluated theoritically and in practice? \\

@@

\subsection{Analysis and Discussion}

@@

RQ5: What domains have RBAC extensions been created for? \\

Business needs have historically driven RBAC research and development.  The primary mode of evaluation for
model extensions has been the presentation of business scenarios in various domains and how the model
uniquely handles those particular scenarios.  Thus, looking for trends in the domains used in the example
scenarios might serve to illuminate a trend worth further examination into the reasaon for the explosion of
RBAC extensions.  The authors identified domains presented within the primary sources by looking for example
scenarios cast within a particular domain or mention of domain requirements within the body of the paper.
We found that the domains mentioned and their associated sources are:

@@

The predominant domain for which extension models have been generated for is that of the medical domain with 9 of 29 mentioning scenarios or requirements of that industry.
Mobile computing and enterprise workflows were each represented by 5 papers claiming to be influenced by the requirements for access control within these domains. The final set
of domains was pervasive computing environments and large-scale organizations with 3 each and web applications with 1.  There were 4 papers without any direct mention of a domain
since Aich et al. \cite{aich09:role} fall under both the medical domain and mobile computing.

\subsection{Analysis and Discussion}

The medical domain produced the largest selection of papers when analyzing the domains influencing the proposals of extension models.  
Further, the authors noted that the categories associated with papers identifying the medical domain was not limited to one or two but cut across
each of the nine categories except for Organization and Resource. 
The cross-category nature of the medical domain papers appears indicative of the complex nature of medical applications and the requirements therein.
Given the growth of the research and development of medical applications over the past decade this result does not appear to be surprising. However,
the RBAC standard was originally created to reduce cost and increase interoperability - two goals of current regulation around the standardization
of electronic health record systems. The large number of proposed models, and the cross-category result stand in direct opposition of the goals
of both the RBAC standard and current regulations.

The RBAC standard has been re-enforced by the economic impact that standardization has had on enterprises needing to apply access control.  The
inclusion of extension models targeted at the enterprise workflow domain is indicative of the expansion of requirements for enterprises. Developers
and researchers should take care when looking at extension models designed to addresses the newer requirements of enterprise workflows in order to
achieve the same economic implementation and maintainability benefits the original standard model presents.

Mobile computing has seen a dramatic increase in the number of available devices, operating systems and applications since 1997 when the first smart phone
was introduced. 
The domain analysis results produced 5 papers that targeted extensions that are designed to address the requirements of mobile computing.
For a domain that was roots in personal and enterprise computing, protecting the data of both through access controls is paramount given their ubiquity.

### 2013-04-03 paper/sections/intro.tex
Adding analysis and discussion of domains.

\begin{itemize}
\setlength{\itemsep}{0.25pt}
\item What categorizations exist within extensions to RBAC?
\item What are the motivations behind extensions to RBAC?
\item Do the extensions to RBAC have corresponding implementations?
\item How are extensions to RBAC evaluated theoritically and in practice?
\item What domains have extensions to RBAC been created for?
\item What commonalities or generalizations exist across all categorizations?
\end{itemize}

>>>>

\begin{itemize}
\setlength{\itemsep}{0.25pt}
\item RQ1: What categorizations exist within extensions to RBAC?
\item RQ2: What are the motivations behind extensions to RBAC?
\item RQ3: Do the extensions to RBAC have corresponding implementations?
\item RQ4: How are extensions to RBAC evaluated theoritically and in practice?
\item RQ5: What domains have extensions to RBAC been created for?
\item RQ6: What commonalities or generalizations exist across all categorizations?
\end{itemize}
